---
title: "R Markdown"
subtitle: "R's Secret Ingredient"
author: Garrick Aden-Buie
location: "Toronto Data Workshop"
date: "2021-02-11"
output:
  xaringan::moon_reader:
    lib_dir: assets/libs
    css: 
      - assets/css/xaringan-rstudio.css
      - assets/css/title-slide.css
    seal: false
    anchor_sections: false
    self_contained: false
    # includes:
    #   after_body: assets/html/extras.html
    nature:
      titleSlideClass: ["bottom", "left"]
      slideNumberFormat: "%current%"
      highlightStyle: false
      highlightLines: false
      ratio: 16:9
      countIncrementalSlides: true
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, width = 70)

knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  hiline = TRUE
)
```

name: title
class: middle hide-count

```{r xaringan-extras, echo=FALSE, results="asis"}
xaringanExtra::use_xaringan_extra(c(
  "tile_view",
  "tachyons",
  "editable"
))
xaringanExtra::use_extra_styles(hover_code_line = FALSE, mute_unhighlighted_code = TRUE)
```

<!-- Title Slide -->
.talk-meta[
.talk-title.center[
# `r rmarkdown::metadata$title`

## .pink.f-pompiere[`r rmarkdown::metadata$subtitle`]
]

<div class="talk-band left">
<div class="talk-author f-zilla">`r rmarkdown::metadata$author`</div>
<div class="talk-twitter code">&commat;grrrck</div>
</div>
<div class="talk-band right">
<div class="code">`r paste(rmarkdown::metadata$location, collapse = ", ")`</div>
<div class="code">`r paste(rmarkdown::metadata$date, collapse = ", ")`</div>
</div>
]

---
background-image: url('https://source.unsplash.com/2LJ4rqK2qfU')
background-size: cover
background-position: center center
background-repeat: no-repeat
class: right top

# What is R Markdown?

(wrong answers only)

.can-edit.f-pen.f2[
one  
two
]
