---
title: Plastic Pollution
subtitle: An {epoxy} example
output: html_document
---

## A basic knitr example

```{r include=FALSE}
rewrite_chunk <- function(label, include_label = FALSE, nbt = 3) {
  chunk <- knitr::knit_code$get(label)
  opts <- attr(chunk, "chunk_opts")
  bt <- strrep("`", nbt)
  engine <- opts$engine
  exclude <- c("engine")
  if (!isTRUE(include_label)) {
    exclude <- c(exclude, "label")
  }
  opts <- opts[setdiff(names(opts), exclude)]
  opts <- paste(
    vapply(names(opts), FUN.VALUE = character(1), function(on) {
      paste0(
        if (on != "label") paste(on, "= "), 
        if (is.character(opts[[on]])) dQuote(opts[[on]], q = 0) else deparse(opts[[on]])
      )
    }),
    collapse = ", "
  )
  header <- paste0(bt, "{", engine, if (length(opts) && nzchar(opts)) " ", opts, "}")
  paste(
    header,
    paste(chunk, collapse = "\n"),
    bt,
    sep = "\n"
  )
}
```


```{r setup, message=FALSE, warning=FALSE, results="hide"}
# remotes::install_github("gadenbuie/epoxy")
library(epoxy)

library(dplyr, warn.conflicts = FALSE)
```

```{r load-plastics, message=FALSE, warning=FALSE, results="hide"}
# https://github.com/rfordatascience/tidytuesday/blob/master/data/2021/2021-01-26/
# https://www.breakfreefromplastic.org/globalbrandauditreport2020/
plastics <- readr::read_csv(here::here("data", "plastics.csv"))


plastics_grand_summary <- 
  plastics %>% 
  group_by(country, year, num_events, volunteers) %>% 
  summarize(
    grand_total = sum(grand_total, na.rm = TRUE),
    .groups = "drop"
  ) %>% 
  arrange(year, desc(grand_total))

plastics_2020_summary <- plastics_grand_summary %>% filter(year == 2020)

n_volunteers <- sum(plastics_2020_summary$volunteers, na.rm = TRUE)
n_countries <- nrow(plastics_2020_summary)
n_audits <- sum(plastics_2020_summary$num_events)
n_pieces <- sum(plastics_2020_summary$grand_total)
```

### Normal R Markdown

````markdown
```{asis}
_Break Free From Plastic_ engaged `r n_volunteers` volunteers in 
`r n_countries` countries to conduct `r n_audits` brand audits. 
These volunteers collected `r n_pieces` pieces of plastic waste.
```
````

_Break Free From Plastic_ engaged `r n_volunteers` volunteers in 
`r n_countries` countries to conduct `r n_audits` brand audits.
These volunteers collected `r n_pieces` pieces of plastic waste.

### With epoxy glue chunk

````markdown
`r rewrite_chunk("glue-example-1")`
````

```{glue glue-example-1}
_Break Free From Plastic_ engaged {n_volunteers} volunteers in 
{n_countries} countries to conduct {n_audits} brand audits. 
These volunteers collected {n_pieces} pieces of plastic waste.
```

## Tracking Updates

### Variables make life easier

```{r echo=TRUE}
knitted_when <- format(Sys.Date())
knitted_where <- knitr::current_input()
knitted_with <- packageVersion("knitr")
knitted_status <- emo::ji("smile")
knitted_doc_url <- downlit::autolink_url("knitr::knit()")
```

`````markdown
```{asis}
Report prepared on `r knitted_when` from ``r knitted_where`` 
with knitr version `r knitted_with` `r knitted_status`. 
Read more about [`knitr::knit()`](`r knitted_doc_url`). 
```
`````

Report prepared on `r knitted_when` from ``r knitted_where`` 
with knitr version `r knitted_with` `r knitted_status`. 
Read more about [`knitr::knit()`](`r knitted_doc_url`).

### Lists make variables easy

```{r echo=TRUE}
knitted <- list(
  when = format(Sys.Date()),
  where = knitr::current_input(),
  with = packageVersion("knitr"),
  status = emo::ji("smile"),
  doc_url = downlit::autolink_url("knitr::knit()")
)
```

`````markdown
```{asis}
Report prepared on `r knitted$when` from ``r knitted$where`` 
with knitr version `r knitted$with` `r knitted$status`. 
Read more about [`knitr::knit()`](`r knitted$doc_url`). 
```
`````

Report prepared on `r knitted$when` from ``r knitted$where`` 
with knitr version `r knitted$with` `r knitted$status`. 
Read more about [`knitr::knit()`](`r knitted$doc_url`).

### Glue makes inline data easier

`````markdown
`r rewrite_chunk("glue-list-example-1")`
`````

```{glue glue-list-example-1, data = knitted}
Report prepared on {when} from `{where}` with knitr version {with} {status}.
Read more about [`knitr::knit()`]({doc_url}).
```

### Another look at our summary sentence

```{r}
n_2020 <-
  plastics_2020_summary %>%
  summarize(
    countries = n(),
    across(c(num_events, volunteers, grand_total), sum, na.rm = TRUE)
  )
```

````markdown
`r rewrite_chunk("glue-2020-example")`
````

```{glue glue-2020-example, data = n_2020}
_Break Free From Plastic_ engaged {volunteers} volunteers in 
{countries} countries to conduct {num_events} brand audits. 
These volunteers collected {grand_total} pieces of plastic waste.
```


## Summarizing

### Multiple Years

```{r}
n_all <-
  plastics_grand_summary %>%
  group_by(year) %>% 
  summarize(
    countries = n(),
    across(c(num_events, volunteers, grand_total), sum, na.rm = TRUE)
  ) %>%
  mutate(across(-(1:2), format, big.mark = ","))

n_all
```

````markdown
`r rewrite_chunk("glue-all-summary")`
````

```{glue glue-all-summary, data = n_all}
- **In {year}**, _Break Free From Plastic_ engaged {volunteers} volunteers in 
  {countries} countries to conduct {num_events} brand audits. 
  These volunteers collected {grand_total} pieces of plastic waste.

```

### Say it boldly

````markdown
`r rewrite_chunk("glue-bold-transformer")`
````

```{glue glue-bold-transformer, data = n_all, .transformer = epoxy_style_bold()}
- In {year}, _Break Free From Plastic_ engaged {volunteers} volunteers in 
  {countries} countries to conduct {num_events} brand audits. 
  These volunteers collected {grand_total} pieces of plastic waste.

```

### As HTML


````markdown
`r rewrite_chunk("glue-html-example")`
````


::: row

```{glue_html glue-html-example, data = top_n(plastics_2020_summary, 6, grand_total)}
<div class="col-sm-6 col-md-4">
  <div class="panel panel-default">
    <div class="panel-heading">
      <h3 class="panel-title">{{country}}</h3>
    </div>
    <div class="panel-body">
      <ul class="list-unstyled">
        <li><strong>Volunteers:</strong> {{volunteers}}</li>
        <li><strong>Events:</strong> {{num_events}}</li>
        <li><strong>Pieces of Plastic:</strong> {{format(grand_total, big.mark = ",")}}</li>
      </ul>
    </div>
  </div>
</div>
```

:::
